\section{Tensor operators} \label{sec:app:tensor-op}
Tensor operators by definition transform like tensors under group action.
In general, a tensor operator of rank transforms as follows:

\begin{align}
    \left(U(R) T U(R)^{-1}\right)_{ij...}  = U(R)_{ia} U(R)_{jb} ... T_{ab...}
\end{align}

By expanding group action around identity, transformation law can be
formulated for corresponding algebra:

\begin{align}
    \left[A(R), T\right]_{ij...} = U(A)_{ia} T_{aj...} + U(A)_{jb} T_{ib...} + ...
\end{align}

Usually tensor operators are classified by rank, a minimal number of vector
operators needed to construct the tensor. It also represents a number of terms
in algebra's transformation law and number of multipliers in group transformation law. 

Assuming the group being a group of 3-rotations we are coming to notion of
a \textit{spherical tensor operator} Corresponding commutation relations are more
convenient for further use when represented in $SU(2)$ form involving ladder operators:

\begin{align}
        &\left[J_{\pm}, T^{(k)}_{q}\right] = \sqrt{k(k+1) - q(q\pm1)} T^{(k)}_{q\pm1} \\
        &\left[J_z, T^{(k)}_{q}\right] = q T_{q}^{(k)}
\end{align}
where $k$ — rank of the operator.

It is easy to build families of operators of specified rank by starting
from $J_{+}^k$ as an operator corresponding to the highest weight $T^{(k)}_k$
and lowering the weight step by step:

\begin{align}
        & \left[J_{+}, T^{(k)}_k\right] = \left[J_{+}, J_{+}^{k}\right] = 0 \\
        & \left[J_{-}, T^{(k)}_k\right] =  \sqrt{k(k+1)-k(k-1)} T^{(k)}_{k-1} \\
        & \dots
\end{align}

For further intuition it is better to review a couple of examples.

\paragraph{Spin-1}

\begin{align}
        & V_1 = \frac{1}{2}S_{+} \\
        & V_0 = -\frac{1}{\sqrt{2}} S_{z} \\
        & V_{-1} = -\frac{1}{2}S_{-}
\end{align}

\paragraph{Spin-2}

\begin{align}
        & V_{\pm2} = \frac{1}{2\sqrt{21}} S_{\pm}^2 \\
        & V_{\pm1} = \mp \frac{1}{2\sqrt{21}} \left\{S_z, S_{\pm}\right\} \\
        & V_0 = \frac{2}{3 \sqrt{14}} \left[S_z^2 - \frac{1}{4} \left\{S_{+}, S_{-}\right\} \right]
\end{align}

\paragraph{Spherical harmonics l=1}
It is an interesting example of how rotational group could act not on itself
but on some other space. Here we have orbital momentum operators acting
on space coordinates. ${x, y, z}$ can be treated as vector operators.
For instance, they can act on itselves building higher rank operators.

Returning back to $l=1$ family contruction, it is easy to check that
$(x+\mathrm{i}y)^{l}$ is an operator of the highest weight. Consequently,
acting on it by $L_{-}$ we'll obtain the whole family.

\begin{align}
        & Y_{\pm1}^{1} = \mp \frac{1}{\sqrt{2}} \frac{x \pm \mathrm{i}y}{r} \\
        & Y_0^1 = \frac{z}{r}
\end{align}

\paragraph{Spherical harmonics l=2}
\begin{align}
        &Y_{\pm2}^{2} = \sqrt{\frac{3}{8}} \frac{(x\pm\mathrm{i}y)^2}{r^2} \\
        &Y_{\pm1}^{2} = \mp \sqrt{\frac{3}{2}} \frac{(x\pm\mathrm{i}y)z}{r^2} \\
        &Y_0^{2} = \frac{1}{\sqrt{8}} \frac{2z^2 - x^2 - y^2}{r^2}
\end{align}

\subsection*{Normalization}
Another crucial point of the algorithm above, that it reproduces families
up to common normalization factor. As we are dealing with linear operators,
there is a way to induct a notion of scalar product from vector space. Thus,
before we start with operators, let's discuss scalar product of vectors.

Let we have vector space $V$ and a space of linear functionals on V --- $V^\star$.
Usually bases of these spaces respect the following condition:

\begin{align}
    \vec{e}^i(\vec{e}_j) = \delta^i_j \quad \vec{e}^i \in V^\star, \vec{e}_j \in V
\end{align}

Also there is a natural way to define how does $V$ act on $V^\star$:

\begin{align}
    \vec{e_i}(\vec{e^j}) = \vec{e^j}(\vec{e_i})
\end{align}

To provide $V$ with scalar product we should define a metric. In this notation
metric $g^\prime$ is a linear map from space to co-space. It should be symmetric
and positve-defined:

\begin{align}
        &g^\prime: V \rightarrow V^\star \\
        &(g^\prime\vec{a})(b) = \vec{a}(g^\prime\vec{b}) = g(\vec{a}, \vec{b}) \\
        & g(\vec{a}, \vec{a}) > 0 \quad \vec{a} \neq \vec{0}
\end{align}

Where we introduced $g$, which is a scalar product:

\begin{align}
    \vec{a}\cdot\vec{b} = g(\vec{a}, \vec{b})
\end{align}

In case of vectors defined on complex field, $g$ is antilinear in respect to the
first argument, by convention. And the product is called pseudo-scalar:

\begin{align}
    (g^\prime\vec{a})^\star(\vec{b}) = g(\vec{a}, \vec{b}) = g(\vec{b}, \vec{a})^\star
\end{align}

$g$ generates a natural map $g_\prime: V^\star \rightarrow V$:

\begin{align}
    g_\prime(\hat{a}) = (g^\prime)^{-1}(\hat{a}) = \vec{a} \quad \hat{a} \in V^\star, \vec{a} \in V
\end{align}

In general, linear operator can be represented as a tensor
living in $V^\star \otimes V$.

\begin{align}
        &T: V \rightarrow V \\
        &T = T_i^j e_j \otimes e^i \quad e^i \in V^\star, e_j \in V 
\end{align}

By analogy with vectors, scalar product of tensors could be defined as follows:

\begin{align}
        &\vec{A}^\prime = A_i^j g_\prime(e_j) \otimes g^\prime(e^i) \\ 
        &\vec{A} \cdot \vec{B} = (\vec{A}^\prime)^\star(\vec{B}) \quad \vec{A}, \vec{B} \in V \otimes V^\prime
\end{align}

Where $\prime-operation$ spreads over basis vectors to flip their nature
between $V$ and $V^\prime$. Together with complex conjugation $\star$, it
defines hermitian conjugation $\dagger$. It is easy to rewrite
scalar product in terms of matrices:

\begin{align}
    \vec{A} \cdot \vec{B} = \vec{A}^\dagger (\vec{B}) = A_{ij}^\star B_{ij} = (A^T)^\star_{j i} B_{ij} = Tr(A^\dagger B)
\end{align}

\paragraph{Consistency}

One can mention that acquired tensor operators are defined up to the prefactor common among family, so states of one family should have the same norm. Let's show that norm defined as above is independent on the member of the family.

\begin{align}
    &\sum_m \bra{J m} T^{(k) \dag}_q T^{(k)}_q \ket{J m} = \sum_{m, m^\prime} \bra{J m} T^{(k) \dag}_q \ket{J m^\prime}\bra{J m^\prime} T^{(k)}_q \ket{J m} = \\
    &=  \sum_{m, m^\prime} \abs{ \bra{J m^\prime} T^{(k)}_q \ket{J m} }^2 = \abs{\bra{J} T^{(k) }\ket{J}}^2 \sum_{m, m^\prime} \braket{J m}{k q J m^\prime} \braket{k q J m^\prime}{J m} = \\
    &= \abs{\bra{J} T^{(k) }\ket{J}}^2 \frac{2J+1}{2k + 1} \sum_{m, m^\prime} \braket{k (-q)}{J (-m) J m^\prime} \braket{J (-m) J m^\prime}{k (-q)} = \\
    &= \frac{2J+1}{2k + 1} \abs{\bra{J} T^{(k) }\ket{J}}^2
\end{align}
